Systematic Review

### 2019-04-18 Source/Thesis/Response.tex

\documentclass[11pt]{article}

\usepackage{setspace}
\onehalfspacing

\usepackage{etoolbox}
\AtBeginEnvironment{quote}{\singlespacing\small\itshape}

\begin{document}
\title{Response to the Qualification Report and Viva Voce feedback}
\maketitle
\par 
\begin{quote}
The student had a very good understanding of the literature and could summarise it well. It was a bit lacking in the machine learning area but he has the capacity for improving that and is aware of what he needs to do. His research background was good but there needed to be more focus on the research questions. These were not explored well in the QR but were much clearer in the viva. He now has some very good ideas to take forward that should lead to a Ph.D.
\par 
\bigskip
The main advice we would give is to be much more careful about how and what data you collect. Getting the participants to do it themselves on a daily basis by, for example, a speech diary that they record and submit, is much more practical than a battery of tests in a clinic. Plus you do not want to be asking about clinical diagnoses using, for example, PHQ9 that measures depression because this raises a lot of ethics issues that will make it harder for NHS ethics approval. Keep the data collection simple, especially as the focus of the Ph.D is about changes in language and not about the cognitive tests themselves. We do not think the latter are necessary because the focus of the Ph.D is on whether you can detect decline by differences in language use over time and not about determining the clinical underpinnings of those differences.
\end{quote}

\subsection*{Aims and Objectives}
The overall objective of my research is to explore whether machine learning and natural language processing can aid in the detection of Mild Cognitive Impairment and Early Alzheimer's through language alone. With this in mind, my research has the following research questions.

\begin{enumerate}
	\item What research has been conducted in this field?
	\item How can we use technology to best enable the collection of language samples?
	\item Can we develop a complete pipeline of that processes data efficiently?
	\item What can machine learning tell us about how language affects us?
\end{enumerate}

\section*{Proposed Methodology}
\subsection*{Stage 1 - Systematic Review of the NLP and Machine Learning research to this problem}
The aim of this stage is to explore, in depth, the literature in this area. As this is a new field, and NLP and Machine Learning advances comparitively quickly, bias is given to more recent research. I aim to convert my existing literature review into a systematic review which is positioned from the Computer Science and Machine Learning perspective. Estimated completion, August 2019. This will form chapter 3 of my thesis. This will also produce a publication.

\subsection*{Stage 2 - Delphi Methodology and developing consensus on how best to collect language samples using technology}
The aim of this stage is to develop, in conjunction with experts, a convergence of ideas on how best to collect language samples using technology. The aim is to provide input from clinicians, technology experts and those using the technology within the homes to find the best protocol, and ideas for how to collect data with the focus on ease of use and non intrusiveness. The aim is to recruit no more than 20 participants with a rough guide of 5 clinicians, 5 technology experts and 10 users. Estimated completion, December 2019. This will form chapter 4 of my thesis.

\subsection*{Stage 3 - Development of a pipeline that processes language data accurately}
The aim of this stage is to build a data pipeline, and test the different technologies such as automated speech recognition software that might have an impact on the quality of the features generated. This is based on research done by Fraser (2015, 2019) who uses off the shelf products (Nuance - Dragon NaturallySpeaking) and open-source technology (Kaldi) as a means of converting speech to text. I would like to include tests of state of the art speech recognition from Google speech-to-text, IBM Watson and Amazon transcribe. This will also address the challenges unique to this population such as how to deal with changes in topic, hesitations, repetitions and so on. This will form chapter 5 of my thesis. The aim is to complete this by December 2019.

\subsection*{Stage 4 - Analysis of DementiaBank dataset, an exploration of existing and novel ways of classification of those with MCI and Early AD.}
The aim of this stage is to explore and identify language features that appear to be more important in the identification and classification of those with MCI and early AD. This stage will build upon the systematic review (stage 1) which, amongst other objectives, aims to identify language features other researchers have identified as useful in this problem. This stage will replicate and validate previous research results and introduce One Class Classification as a new way of classifying those with MCI and AD. This will form chapter 6 of my thesis. This should produce a publication. The aim is to complete this by March 2020.

\subsubsection*{One Class Classification}
The prevalence of Dementia in the UK's population is roughly 1 in 14 or 7\%. The prevalence of MCI has only briefly been explored, however some research by a team at the Univesity of Leeds indicate that the prevalence of MCI is between 3.2 - 24\%, and found that the prevalence of MCI in people who have self-reported memory problems is almost double (18\%) the amount of do not self report. Whilst this means that it is entirely possible to recruit a cohort with MCI and AD, it is comparatively costly in terms of time and resources. Given that, from a statistical perspective, this is a highly imbalanced population we can look at the problem as a kind of anomaly detection. This has some precedent in the field of Medicine, where examples of the 'positive' class can be costly or difficult to obtain. 
\par 
One-class classifiers analyze only examples of the majority class (in this case - Healthy Older Adults) to learn a classification boundary that excludes outlier examples. When dealing with heavily imbalanced datasets with text classifcation as an objective, the one-class classifier approach has been demonstrated to outperform conventional two-class classification.  T

\subsection*{Stage 5 - Pilot study of the methodology developed}
The aim of this stage is to pilot the methodology developed in stage 2. Over a period of six months, 10 participants engage in collection of data and we analyse the results from both the participants perspective and the perspective of the researcher. From the participants perspective, we look at whether the process is comfortable, unintrusive and easy to use for the participant. From the researchers perspective, we look at the quality of the audio and whether there are any problems in the data pipeline. We also look at the quantity of language samples and whether the amount of language generated is enough for analysis. This will form chapter 7 of my thesis. This should produce a publication. The aim is to complete this by September 2020.
\end{document}

### 2019-04-19 Source/Systematic Review/Systematic Review.tex
updated systematic review

\subsection{Study selection}
The first step of the study selection was the execution of an evaluation round with 100 random papers from the 593 results returned from the automated searches. These had their title and abstracts assessed by A1, A2 and A3, according to inclusion and exclusion criteria defined previously in the protocol (see Table 2). This step was mainly concerned in maintaining the consistency of the selection between the participants throughout the SLR. The remaining 493 results had their title and abstracts assessed by A1 and A2, according to the inclusion and exclusion criteria. After the evaluations, 37 papers were selected. Then a one-iteration backward snowballing was carried out looking for possible additional studies. The 1199 new identified studies were assessed analogously as the previous ones, resulting in 41 new selected papers. Throughout the whole selection process, A3 and A4 acted in conflict resolution in the case where A1 and A2 couldn’t reach an agreement.
\par 
In total, 78 papers were selected to be fully read and assessed regarding its eligibility. The ones that successfully passed the established criteria previously defined in the protocol, had their relevant data extracted. In order to minimize the chance of selecting studies with bias evidence, a quality assessment questionnaire was used. This questionnaire was adapted from Kitchenham’s guidelines and can be found in the SLR protocol. If the grading attributed to a paper fell below 8 points (out of a total of 12), it would be rejected for quality reasons. The 8-point threshold was
decided in the research group discussions involving all the authors. In this phase, a paper could also be rejected due to inclusion and exclusion criteria because the selection process adopted an inclusive approach. This means that during the reading of the titles and abstracts, in the case where the information provided was incomplete or too general it was selected to be fully read in the posterior phase. A common example is the case when the data analysis technique specified in the abstract was merely “classification”, so it was not possible to know if any machine learning occurred.
\par
As in the study selection, a quality assessment evaluation round was performed beforehand to ensure consistency in the evaluations. A1, A2 and A5 participated in this task. In total, 37 studies composed the final set of included primary studies and had their relevant data extracted, 7 papers were rejected due quality reasons, and 34 papers were rejected due to failing the inclusion and exclusion criteria. One reason for the high number of the latter was the decision to exclude the papers that used solely statistical methods as data analysis tech- niques to build the prognostic models. The selected studies were also assessed for the risk of cumulative evidence bias. This was done by checking, in the case of the same research group with different studies in the final set of included primary studies, if it was justified having both studies (i.e different samples).

@@

\begin{table}
	\begin{tabular}{ p{6cm} | p{6cm} }
	\hline
	Inclusion Criteria & Exclusion Criteria \\ \hline
	Be a primary study in English; AND address research on dementia and comorbidities; AND address at least one ML or MS technique; AND address a prognosis related to dementia and comorbidities. &
	Be a secondary or tertiary study; OR be written in another language other than English; OR do not address a research on dementia and comorbidities; OR do not address at least one ML or MS technique; OR do not address a prognosis related to dementia and comorbidities. \\
	\hline 
	\end{tabular}
	\caption[Table caption text]{Inclusion and Exclusion Criteria}
	\label{table:name}
\end{table}

@@

\begin{tikzpicture}[node distance=2cm]

\node (start) [startstop] {Start};
\node (in1) [io, below of=start] {Input};
\node (pro1) [process, below of=in1] {Process 1};
\node (dec1) [decision, below of=pro1, yshift=-0.5cm] {Decision 1};
\node (pro2a) [process, below of=dec1, yshift=-0.5cm] {Process 2a text text text text text text text text text text};
\node (pro2b) [process, right of=dec1, xshift=2cm] {Process 2b};
\node (out1) [io, below of=pro2a] {Output};
\node (stop) [startstop, below of=out1] {Stop};

\draw [arrow] (start) -- (in1);
\draw [arrow] (in1) -- (pro1);
\draw [arrow] (pro1) -- (dec1);
\draw [arrow] (dec1) -- node[anchor=east] {yes} (pro2a);
\draw [arrow] (dec1) -- node[anchor=south] {no} (pro2b);
\draw [arrow] (pro2b) |- (pro1);
\draw [arrow] (pro2a) -- (out1);
\draw [arrow] (out1) -- (stop);
\end{tikzpicture}
\caption[Figure caption text]{PRISMA flow chart.}
\label{figure:name}
\end{figure}
\subsection{Language Analysis of Speakers with Dementia of the Alzheimer's Type - Guinn and Habash (2012)}

>>>>

\begin{table}
	\begin{tabular}{ p{3cm} | p{3cm} | p{3cm} | p{3cm} }
	\hline
	Scopus & Web of Science & PubMed & IEEE Xplore \\ \hline
	1002 & 991 & 376 & 230 \\ 
	\hline
	\end{tabular}
	\caption[Table caption text]{Totals from each database}
	\label{table:name}
\end{table}

\subsection{Study selection}
A total of 2599 papers were identified through the searches conducted above. Papers that were duplicated were removed and Papers were then evaluated by the JA based on the inclusion and exclusion criteria defined previously (see Table 6). Where JA could not reach a decision, PS and GV were consulted and majority vote on inclusion was conducted. Each paper was initially presented with just the title and the abstract.

\begin{table}
	\begin{tabular}{ p{6cm} | p{6cm} }
	\hline
	Stage & Papers remaining\\ \hline
	Start & 2599 \\ \hline
	Duplicates & Non-papers removed & 2599 \\hline 
	\hline
	\end{tabular}
	\caption[Table caption text]{Totals at each stage}
	\label{table:name}
\end{table}

After the evaluations, 37 papers were selected. Then a one-iteration backward snowballing was carried out looking for possible additional studies. The 1199 new identified studies were assessed analogously as the previous ones, resulting in 41 new selected papers. Throughout the whole selection process, A3 and A4 acted in conflict resolution in the case where A1 and A2 couldn’t reach an agreement.
\par 
In total, 78 papers were selected to be fully read and assessed regarding its eligibility. The ones that successfully passed the established criteria previously defined in the protocol, had their relevant data extracted. In order to minimize the chance of selecting studies with bias evidence, a quality assessment questionnaire was used. This questionnaire was adapted from Kitchenham’s guidelines and can be found in the SLR protocol. If the grading attributed to a paper fell below 8 points (out of a total of 12), it would be rejected for quality reasons. The 8-point threshold was
decided in the research group discussions involving all the authors. In this phase, a paper could also be rejected due to inclusion and exclusion criteria because the selection process adopted an inclusive approach. This means that during the reading of the titles and abstracts, in the case where the information provided was incomplete or too general it was selected to be fully read in the posterior phase. A common example is the case when the data analysis technique specified in the abstract was merely “classification”, so it was not possible to know if any machine learning occurred.
\par
As in the study selection, a quality assessment evaluation round was performed beforehand to ensure consistency in the evaluations. A1, A2 and A5 participated in this task. In total, 37 studies composed the final set of included primary studies and had their relevant data extracted, 7 papers were rejected due quality reasons, and 34 papers were rejected due to failing the inclusion and exclusion criteria. One reason for the high number of the latter was the decision to exclude the papers that used solely statistical methods as data analysis tech- niques to build the prognostic models. The selected studies were also assessed for the risk of cumulative evidence bias. This was done by checking, in the case of the same research group with different studies in the final set of included primary studies, if it was justified having both studies (i.e different samples).

A search of the literature was conducted using ProQuest (PsychArticles), SCOPUS, Web of Science. The following results were found (Table 1). All papers were then reviewed for relevance by reading the abstract and full text where appropriate and a shortlist was compiled. An additional search through references of shortlisted papers was also conducted and any papers who upon further review appeared relevant were added to the shortlist. Papers were included where researchers used machine learning to classify participants as MCI, AD or Healthy using language. We excluded any papers that focused on other forms of dementia or cognitive impairment, as well as any papers in which the language being analysed was not English.

@@

\begin{table}
	\begin{tabular}{ p{6cm} | p{6cm} }
	\hline
	Inclusion Criteria & Exclusion Criteria \\ \hline
	Be a primary study in English; AND address research on dementia and comorbidities; AND address at least one ML or MS technique; AND address a prognosis related to dementia and comorbidities; AND use cognition or language decline as a factor for analysis. &
	Be a secondary or tertiary study; OR be written in another language other than English; OR do not address a research on dementia and comorbidities; OR do not address at least one ML or MS technique; OR do not address a prognosis related to dementia and comorbidities. \\
	\hline 
	\end{tabular}
	\caption[Table caption text]{Inclusion and Exclusion Criteria}
	\label{table:name}
\end{table}

@@

\begin{tikzpicture}[sibling distance = 10em,
	every node/.style = {shape = rectangle, rounded corners,
	draw, align = center, 
	top color = white, bottom color=blue!20}]]

\end{tikzpicture}
\caption[Figure caption text]{PRISMA flow chart.}
\label{figure:name}
\end{figure}
\subsection{Language Analysis of Speakers with Dementia of the Alzheimer's Type - Guinn and Habash (2012)}
